Resources for Data-Driven \\Search-Based Software Engineering

### 2018-01-20 doc/tex/msr18/main.tex
Updates from ShareLaTeX

\begin{document}
\title{
% Research and Teaching Tools for 
Resources for Data-Driven Search-Based Software Engineering}
% \titlenote{Produces the permission block, and
%   copyright information}
% \subtitle{Extended Abstract}
% \subtitlenote{The full version of the author's guide is available as
%   \texttt{acmart.pdf} document}

\author{Vivek Nair, everyone else, Tim Menzies}
\affiliation{%
  \institution{North Carolina State University, USA}
  \city{Raleigh} 
  \state{NC} 
  \postcode{27606}
}
\email{}

@@

XXX optimisation

>>>>

\begin{document}
\title{
% Research and Teaching Tools for 
Resources for Data-Driven \\Search-Based Software Engineering}
% \titlenote{Produces the permission block, and
%   copyright information}
% \subtitle{Extended Abstract}
% \subtitlenote{The full version of the author's guide is available as
%   \texttt{acmart.pdf} document}

\author{Vivek Nair, George Mathew, Jianfeng Chen, Markus Wanger, Leando Minku, Tim Menzies}
\affiliation{%
  \institution{North Carolina State University, USA}
  \city{Raleigh} 
  \state{NC} 
  \postcode{27606}
}
\email{}

@@

\begin{figure*}[!t]
{\center
\includegraphics[width=5.5in]{img/page1.png}}
\caption{http://tiny.cc/sbse = our Github-based repository for resources relating to data-drive Search-based SE 
currently contains 89 artifacts divided into 13 groups. References in the right-hand column come from this paper.
For each of the above, there exists papers showing published baselines. Each of these baselines can be viewed as challenge problems:
how many of these baselines can you repeat/ improve/ refute? To contribute, researchers need only modify the repository then submit a pull request. }
\end{figure*}
XXX optimisation
